Revisiting the hydrodynamic modulation of short surface waves by longer waves

### 2025-06-17 paper.tex
Fix affil. numbers
Fix omitted parentheses in (A 22); Clarify truncation order on L798

\documentclass[lineno]{jfm}

@@

\author{
  Milan Curcic\aff{1}
  \corresp{\email{mcurcic@miami.edu}}
}

@@

\begin{equation}
  \frac{\partial}{\partial t} \left[ N + \mathcal{O}(\varepsilon^4) \right] +
  \frac{\partial}{\partial x} \left[ (C_g + \mathcal{O}(\varepsilon^2)) N + \mathcal{O}(\varepsilon^4) \right] = 0
\end{equation}
Due to the $\mathcal{O}(\varepsilon^2)$ correction to the group speed, the
overall truncation error for the wave action balance is $\mathcal{O}(\varepsilon^2)$
as well:

@@

In summary, asymptotically consistent sets of dispersion and action conservation
equations vary depending on the level of nonlinearity considered.
In the case of linear waves, the dispersion relation (\ref{eq:dispersion}),
the averaged Lagrangian (\ref{eq:averaged_lagrangian_deep_water}), the adiabatic
quantity (\ref{eq:adiabatic1}) and the wave action conservation
(\ref{eq:wave_action_conservation_nonlinear}) are asymptotically consistent.
For third-order Stokes waves, the dispersion relation
(\ref{eq:dispersion_nonlinear}), the adiabatic quantity (\ref{eq:adiabatic2}),
together with the group speed that includes a $\mathcal{O}(\varepsilon^2)$ correction,
are governed by the action conservation law
(\ref{eq:wave_action_conservation_nonlinear}) and are asymptotically consistent.
This is summarized in Table \ref{table:asymptotic_consistency}.

>>>>

\documentclass[lineno]{jfm}
%\documentclass[]{jfm}

@@

\author{
  Milan Curcic\aff{1,2}
  \corresp{\email{mcurcic@miami.edu}}
}

@@

\begin{equation}
  \frac{\partial}{\partial t} \left[ N + \mathcal{O}(\varepsilon^4) \right] +
  \frac{\partial}{\partial x} \left[ (C_g + \mathcal{O}(\varepsilon^2)) (N + \mathcal{O}(\varepsilon^4)) \right] = 0
\end{equation}
Due to the $\mathcal{O}(\varepsilon^2)$ correction to the group speed, the
overall truncation error for the wave action balance is $\mathcal{O}(\varepsilon^2)$
as well:

@@

In summary, asymptotically consistent sets of dispersion and action conservation
equations vary depending on the level of nonlinearity considered.
In the case of linear waves, the dispersion relation (\ref{eq:dispersion}),
the averaged Lagrangian (\ref{eq:averaged_lagrangian_deep_water}), the adiabatic
quantity (\ref{eq:adiabatic1}) and the wave action conservation
(\ref{eq:wave_action_conservation_nonlinear}) are asymptotically consistent.
For third-order Stokes waves, the dispersion relation
(\ref{eq:dispersion_nonlinear}), the adiabatic quantity (\ref{eq:adiabatic2}),
together with the group speed that includes a $\mathcal{O}(\varepsilon^2)$ correction,
are governed by the action conservation law
(\ref{eq:wave_action_conservation_nonlinear}, but with the truncation error of
$\mathcal{O}(\varepsilon^4)$), and are asymptotically consistent.
This is summarized in Table \ref{table:asymptotic_consistency}.
